
# Reproducible Research - Courser Project 1


## loading and preprocessing the data

```{r, echo = TRUE}
library(ggplot2)
activities <- read.csv("activity.csv")
activities$date <- as.Date(activities$date)
```

## What is mean total number of steps taken per day
1. Calculate the total number of steps taken per day

as we can se the number of days is 53
```{r, echo = TRUE}
steps <- aggregate(steps ~ date, data = activities, sum, na.rm = TRUE)
length(steps$date)
```
2. Make a histogram of the total number of steps taken each day

i divide the breack of the histogram by one day i mean y break it in 53 columns 
```{r, echo = TRUE}
hist(x = steps$steps, col = "blue", breaks = 53)
```
3. show mean an median using summary
```{r, echo = TRUE}
mean(steps$steps)
median(steps$steps)
```

## What is the average daily activity pattern?

1. Make a time series plot (i.e. ???????????????? = "????") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo = TRUE}
mean_per_day <- tapply(activities$steps, activities$interval, mean, na.rm = TRUE)
plot(mean_per_day, type="l", col="blue")
```
2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo = TRUE}
names(which.max(mean_per_day))
```

## Imputing missing values

1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with ????????s

```{r, echo = TRUE}
sum(!complete.cases(activities))
```

2. Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

i will find the rows with missing values in steps and replace with the mean of the entire row

3. Create a new dataset that is equal to the original dataset but with the missing data filled in.

```{r, echo = TRUE}
activitiesNA <- activities
activitiesNA$steps <- activitiesNA$steps[is.na(activitiesNA$steps)] <- mean(activitiesNA$steps, na.rm = TRUE)
```


```{r, echo = TRUE}
steps2 <- aggregate(steps ~ date, data = activitiesNA, sum, na.rm = TRUE)
hist(x = steps2$steps, col = "blue")
```




